[Re] Modeling GABA Alterations in Schizophrenia: A Link Between Impaired Inhibition and Gamma and Beta Auditory Entrainment

### 2017-06-20 article/Metzner-2017.tex
defined epsc and eta

The model was implemented solely from the paper description, since the
original code is not publicly available. The model is a simple model
consisting of two neural populations (excitatory and inhibitory cells).
Individual cells are modeled as theta neurons (for a detailed discussion
of this neuron model see \autocite{Boergers2003}). The neuron is
described by a single variable \(\theta\), which can be regarded as the
neuron state, subject to the following dynamics

\[\frac{d \theta}{dt}=1-\cos \theta + (b+S+N(t))\cdot(1+ \cos \theta),\]

@@

where \(\tau _j\) is the synaptic decay time and \(\tau_R\) the synaptic
rise time. The network receives excitatory drive input at click train
frequency from a single pacemaker cell. Additionally, Poissonian noise
input is also given to all cells in the network. A noise spike at time
\(t_n\) elicits the following `EPSC'

>>>>

The model was implemented solely from the paper description, since the
original code is not publicly available. The model is a simple model
consisting of two neural populations (excitatory and inhibitory cells).
Individual cells are modeled as theta neurons (for a detailed discussion
of this neuron model see \autocite{Boergers2003}). The $k$th neuron in a network is
described by a single variable \(\theta_k\), which can be regarded as the
neuron state, subject to the following dynamics

\[\frac{d \theta_k}{dt}=1-\cos \theta_k + (b+S_k+N(t))\cdot(1+ \cos \theta_k),\]

@@

where \(\tau _j\) is the synaptic decay time, \(\tau_R\) the synaptic
rise time and \(\eta\) is a scaling parameter. The network receives excitatory drive input at click train
frequency from a single pacemaker cell. Additionally, Poissonian noise
input is also given to all cells in the network. A noise spike at time
\(t_n\) elicits the following excitatory postsynaptic potential (`EPSC')
